FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-16 NewVersion/paper.tex
Added author info. Move appendix in front of refs (as required?)

 \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
 \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
 \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
 \newcommand\marcoT[1]{\authorText{blue}{#1}}
 \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

%\newcommand\bruno[1]{}
%\newcommand\yanlin[1]{}
%\newcommand\marco[1]{}
%\newcommand\haoyuan[1]{}

@@

% \authorinfo{NoAuthor}
%            {The University of Hong Kong, China}
% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
% %\authorinfo{Marco Servetto}
% %          {Victoria University of Wellington, New Zealand}
% %          {marco.servetto@ecs.vuw.ac.nz}
\author{Authors Omitted}

\institute{}

@@

This paper presents a new model called \emph{\textbf{F}eatherweight
  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
unintentional method conflicts.  In our new model, which is partly
inspired by C++, conflicting methods arising from unrelated methods
can coexist in the same class, and \emph{hierarchical dispatching}
supports unambigous lookups in the presence of such conflicting
methods.  To avoid ambiguity, hierarchical information is employed in
method dispatching, which uses a combination of static and dynamic
type information to choose the implementation of a method at run-time.
Furthermore, unlike all existing inheritance models, our model
supports \emph{hierarchical method overriding}: that is, methods can
be \emph{independently overridden} along the multiple inheritance
hierarchy. We give illustrative examples of our language and features
and formalize \name{} as a minimal Featherweight-Java style calculus.

@@

% \newpage
% \clearpage
% \bibliographystyle{abbrvnat}
\bibliographystyle{splncs03}
\bibliography{paper}

@@

>>>>

%\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
%\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
%\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
%\newcommand\marcoT[1]{\authorText{blue}{#1}}
%\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

\newcommand\bruno[1]{}
\newcommand\yanlin[1]{}
\newcommand\marco[1]{}
\newcommand\haoyuan[1]{}

@@

% \authorinfo{NoAuthor}
%            {The University of Hong Kong, China}
% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
% %\authorinfo{Marco Servetto}
% %          {Victoria University of Wellington, New Zealand}
% %          {marco.servetto@ecs.vuw.ac.nz}
\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{ylwang@cs.hku.hk, hyzhang@cs.hku.hk, bruno@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}

@@

This paper presents a new model called \emph{\textbf{F}eatherweight
  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
unintentional method conflicts.  In our new model, which is partly
inspired by C++, conflicting methods arising from unrelated methods
can coexist in the same class, and \emph{hierarchical dispatching}
supports unambiguous lookups in the presence of such conflicting
methods.  To avoid ambiguity, hierarchical information is employed in
method dispatching, which uses a combination of static and dynamic
type information to choose the implementation of a method at run-time.
Furthermore, unlike all existing inheritance models, our model
supports \emph{hierarchical method overriding}: that is, methods can
be \emph{independently overridden} along the multiple inheritance
hierarchy. We give illustrative examples of our language and features
and formalize \name{} as a minimal Featherweight-Java style calculus.

@@

% \newpage
% \clearpage
% \bibliographystyle{abbrvnat}

@@

\newpage

\bibliographystyle{splncs03}
\bibliography{paper}

### 2017-10-16 NewVersion/sections/Conclusion.tex
Added author info. Move appendix in front of refs (as required?)

This paper proposes \MIM{} as a formalized multiple inheritance model for
unintentional method conflicts. Previous approaches 
either do not support unintentional method conflicts, have to
compromise between code reuse and type safety, or do not fully support
overriding in the presence of unintentional conflicts. To deal with unintentional method conflicts we
introduce two key mechanisms: hierarchical dispatching and
hierarchical overriding. Hierarchical dispatching is inspired by the
mechanisms in C++. We provide a minimal formal model of hierarchical
dispatching in \MIM{}. Such algorithm makes use of both dynamic type
information and path information from either upcasts or parameters'
information. Such an approach not only offers great code reuse like
dynamic dispatch but also ensures unambiguity by our algorithm for
method resolution. Additionally we introduce \emph{hierarchical
  overriding} to allow conflicting methods in different branches to be
individually overriden.

\MIM{} is formalized following the style of
Featherweight Java and type-soundness is proved. A prototype language is
implemented in Scala as a simple interpreter. We believe that the formalization of
hierarchical dispatching features is general and
can be safely embedded to other OO models, so as to have support for the triangle
inheritance.

Our model can certainly be improved at some aspects. 
As discussed in Section~\ref{sec:discussion}, there are orthogonal and
non-orthogonal features that can potentially be added to the design space. 
The future work relates to loosening the model without giving up its soundness,
together with more exploration on fields in the multiple inheritance setting.

>>>>

This paper proposes \MIM{} as a formalized multiple inheritance model for
unintentional method conflicts. Previous approaches 
either do not support unintentional method conflicts, thus have to
compromise between code reuse and type safety, or do not fully support
overriding in the presence of unintentional conflicts. To deal with unintentional method conflicts we
introduce two key mechanisms: hierarchical dispatching and
hierarchical overriding. Hierarchical dispatching is inspired by the
mechanisms in C++. We provide a minimal formal model of hierarchical
dispatching in \MIM{}. Such algorithm makes use of both dynamic type
information and path information from either upcasts or parameters'
information. It not only offers great code reuse like
dynamic dispatch but also ensures unambiguity by our algorithm for
method resolution. Additionally we introduce \emph{hierarchical
  overriding} to allow conflicting methods in different branches to be
individually overridden.

\MIM{} is formalized following the style of
Featherweight Java and proved to be sound. A prototype interpreter is
implemented in Scala. We believe that the formalization of
hierarchical dispatching features is general and
can be safely embedded in other OO models, so as to have support for the triangle
inheritance.

Our model can certainly be improved in some aspects. 
As discussed in Section~\ref{sec:discussion}, there are orthogonal and
non-orthogonal features that can potentially be added to the design space. 
The future work relates to loosening the model without giving up its soundness,
together with more exploration on supporting fields in the multiple inheritance setting.

### 2017-10-16 NewVersion/sections/Discussion.tex
Added author info. Move appendix in front of refs (as required?)

Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
to include only method declarations, and those abstract methods can be implemented in a class body. 
The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of its orthogonality
to the core calculus. In traits the
similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
Abstract methods provide a way to
delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.

@@

Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
Other languages support more complicated behaviour.
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
that case for two reasons. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract. Thus our model adopts a very conservative behaviour rather than automatically merging 
methods, and implicitly assumming diamond inheritance. 
It is possible to change our model to account for other behaviour for abstract methods, but we view this as a mostly 
orthogonal change to our work, that should not affect the essence of the model presented here.

@@

One typical non-orthogonal extension to \MIM{} could be to have fields.
The design of \MIM{} can be viewed as an variant of Java 8 with default methods which allows for unintentional method conflicts.
Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue. There has been some related work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}. In our model, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. However such an extension requires more though, so we leave it to future work.

@@

\vspace{3pt}\begin{lstlisting}
interface A { void m() {...} }
interface B extends A { void m() {...} }
interface C extends A { void m() {...} }
interface D extends B, C {}
\end{lstlisting}\vspace{3pt}
In the example, both $B.m$ and $C.m$ override $A.m$. In the example, D inherits
both conflicting methods without an explicit override. In this case automatically merging 
the two methods (to achieve diamond inheritance) is not possible, which is why many 
models (like traits and Java 8) reject such programs. Moreover, keeping the two 
method implementations in \lstinline|D| is problematic. 
In essence, hierarchical information is 
not helpful to disambiguate later method calls, since the two methods share 
the same origin (\lstinline|A.m|). 
Our calculus rejects such conflicts by the \textsc{(T-Intf)} rule, where $D$ is considered to be ill-formed. 
We believe that rejecting \lstinline|D| follows the principle of models like traits and Java 8 interfaces, 
where the language/type-system is meant to alert the programmer for a possible conflict.

>>>>

Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
to include only method declarations, and those abstract methods can be implemented in a class body. 
The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of the orthogonality
to the core calculus. In traits the
similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
Abstract methods provide a way to
delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.

@@

Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
Other languages may support more complicated behaviours.
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
that case for two reasons. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract. Thus our model adopts a very conservative behaviour rather than automatically merging 
methods, and implicitly assuming diamond inheritance. 
It is possible to change our model to account for other behaviours for abstract methods, but we view this as a mostly 
orthogonal change to our work, that should not affect the essence of the model presented here.

@@

One typical non-orthogonal extension to \MIM{} could be to have fields.
The design of \MIM{} can be viewed as a variant of Java 8 with default methods which allows for unintentional method conflicts.
Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue. There has been some related work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}. In our model, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. However such an extension requires more thoughts, so we leave it to future work.

@@

\vspace{3pt}\begin{lstlisting}
interface A { void m() {...} }
interface B extends A { void m() {...} }
interface C extends A { void m() {...} }
interface D extends B, C {}
\end{lstlisting}\vspace{3pt}
Here both $B.m$ and $C.m$ override $A.m$, and D inherits
both conflicting methods without an explicit override. In this case automatically merging 
the two methods (to achieve diamond inheritance) is not possible, which is why many 
models (like traits and Java 8) reject such programs. Moreover, keeping the two 
method implementations in \lstinline|D| is problematic. 
In essence, hierarchical information is 
not helpful to disambiguate later method calls, since the two methods share 
the same origin (\lstinline|A.m|). 
Our calculus rejects such conflicts by the \textsc{(T-Intf)} rule, where $D$ is considered to be ill-formed. 
We believe that rejecting \lstinline|D| follows the principle of models like traits and Java 8 interfaces, 
where the language/type-system is meant to alert the programmer for a possible conflict.

### 2017-10-16 NewVersion/sections/Introduction.tex
typos
Added author info. Move appendix in front of refs (as required?)

\yanlin{
TODOs:
\begin{itemize}
\item UML Diagram for full solution in introduction with informal explanation
\item Move Figure 5 to end of Section 2 together with explanation
\item Improve Figure 5 with additional mbody calls
\item Improve Figure 5 with visual information that signals that in examples d) and e) then D does not type-check
\item Make names of classes more consistent in Figure 5
\item Add example (f) : A m      B m   C m   D  m  This would compile, note that if it was BArrowA m and/or CArrowA m it would also compile and D would have the same observable behaviour
\item remove S1 “Unfortunately, such an issue ...”
\item (\checkmark)S2, should remove the discussion about JFrmae. all return type void.
\item (\checkmark)S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
\item (\checkmark)S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“. and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw. “.
\item S2.2 revise paragraph “Implicit and Explicit Upcasts “.
\item S2.3 (Maybe) put “Potential solutions/workarounds in existing languages” after “FHJ solution”.
\item S2.3 (Maybe) add “redraw()” method in Drawable. and add another method call similar to shuffleAndDraw()
\item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker

\item (\checkmark)in Figure 1, the UML diagram on the right side is not quite right, 
we want to be able to override draw from Drawable in DrawableSafeDeck, 
the override (which is *the most important point*) is not in the UML diagram.
  => Figure 1 on the right is the UML for P3 potential workaround, not for P3 FHJ, we need another UML. 
\item Submit abstract
\item Introduction to revise (by Bruno)
\item Revise overview (Yanlin and Haoyuan)
\item Section 4, 5 (Haoyuan)
\item Section 6 (Yanlin)
\item Section 7 (Yanlin and Haoyuan)
\end{itemize}
}

@@

In contrast to diamond inheritance, a second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
methods that do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but happen to have the same names (and signatures).
A simple example of this situation is two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context, the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicting methods have very different meanings and do not share a
common parent. We call such a case \textit{triangle inheritance}, in
analogy to diamond inheritance.

@@

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows
this by interface multiple inheritance and explicit method
implementations. But since C\# is a single inheritance language, 
it is only possible to \emph{implement} multiple interfaces (but not
multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts triangle inheritance and
resolves the ambiguity by specifying the expected path by
\emph{upcasts}. However
neither the C\# or C++ approaches allow
such conflicting methods to be further overriden. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

\textit{Hierarchical overriding} is a novel language
mechanism that allows method overriding to be applied
only to one branch of the class hierarchy. Hierarchical overriding 
adds expressive power that is not available in languages such as 
C++ or C\#. Hierarchical overriding allows overriding to work 
for classes with multiple (conflicting) methods sharing the 
same names and signatures. An example is presented in 
Figure~\ref{fig:main}. In this example there are 4 classes/interfaces.
Two classes model a deck of cards (\lstinline|Deck|) and a class for
drawable widgets (\lstinline|Drawable|). 
A class \lstinline|SafeDeck| adds functionality to check whether a 
the deck is empty and to prevent drawing a card from an empty deck. 
The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierchical
overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
methods for each parent, but overriding \emph{only} the \lstinline|draw|
method coming from \lstinline|Drawable|, in order to draw a widget
with a deck of cards. Note that hierchical overriding is denoted in the UML
diagram with the notation
\lstinline|draw()|$\shneg$\lstinline|Drawable|. In this case the
notation expresses that the \lstinline|draw| method from \lstinline|Drawable|
is overriden. Although in this example only one of the
\lstinline|draw| methods is overriden (and the other is simply inherited), hierarchical overriding
supports multiple conflicting methods to be independently overriden as well.

To present hierarchical overriding and dispatching, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness.

%%Our model can be viewed as
%%a generalization of the simplified trait model by providing additional support to
%%the triangle inheritance.

In summary, our contributions are:
\begin{itemize}
	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility in the presence
        of unintentional method conflicts.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics, and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} implemented in Scala.
          \bruno{Are the examples in the paper implemented in the interpreter?}
          \yanlin{new formalization has not been implemented yet.}
\end{itemize}

>>>>

\begin{comment}
\yanlin{
TODOs:
\begin{itemize}
\item UML Diagram for full solution in introduction with informal explanation
\item Move Figure 5 to end of Section 2 together with explanation
\item Improve Figure 5 with additional mbody calls
\item Improve Figure 5 with visual information that signals that in examples d) and e) then D does not type-check
\item Make names of classes more consistent in Figure 5
\item Add example (f) : A m      B m   C m   D  m  This would compile, note that if it was BArrowA m and/or CArrowA m it would also compile and D would have the same observable behaviour
\item remove S1 “Unfortunately, such an issue ...”
\item (\checkmark)S2, should remove the discussion about JFrmae. all return type void.
\item (\checkmark)S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
\item (\checkmark)S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“. and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw. “.
\item S2.2 revise paragraph “Implicit and Explicit Upcasts “.
\item S2.3 (Maybe) put “Potential solutions/workarounds in existing languages” after “FHJ solution”.
\item S2.3 (Maybe) add “redraw()” method in Drawable. and add another method call similar to shuffleAndDraw()
\item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker

\item (\checkmark)in Figure 1, the UML diagram on the right side is not quite right, 
we want to be able to override draw from Drawable in DrawableSafeDeck, 
the override (which is *the most important point*) is not in the UML diagram.
  => Figure 1 on the right is the UML for P3 potential workaround, not for P3 FHJ, we need another UML. 
\item Submit abstract
\item Introduction to revise (by Bruno)
\item Revise overview (Yanlin and Haoyuan)
\item Section 4, 5 (Haoyuan)
\item Section 6 (Yanlin)
\item Section 7 (Yanlin and Haoyuan)
\end{itemize}
}
\end{comment}

@@

In contrast to diamond inheritance, a second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
methods do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but happen to have the same names (and signatures).
A simple example of this situation is two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context, the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicting methods have very different meanings and do not share a
common parent. We call such a case \textit{triangle inheritance}, in
analogy to diamond inheritance.

@@

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows
this by interface multiple inheritance and explicit method
implementations. But since C\# is a single inheritance language, 
it is only possible to \emph{implement} multiple interfaces (but not
multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts triangle inheritance and
resolves the ambiguity by specifying the expected path by
\emph{upcasts}. However
neither the C\# or C++ approaches allow
such conflicting methods to be further overridden. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

\textit{Hierarchical overriding} is a novel language
mechanism that allows method overriding to be applied
only to one branch of the class hierarchy. Hierarchical overriding 
adds expressive power that is not available in languages such as 
C++ or C\#. Hierarchical overriding allows overriding to work 
for classes with multiple (conflicting) methods sharing the 
same names and signatures. An example is presented in 
Figure~\ref{fig:main}. In this example there are 4 classes/interfaces.
Two classes model a deck of cards (\lstinline|Deck|) and a class for
drawable widgets (\lstinline|Drawable|). 
The class \lstinline|SafeDeck| adds functionality to check whether the
deck is empty and to prevent drawing a card from an empty deck. 
The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierarchical
overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
methods for each parent, but overriding \emph{only} the \lstinline|draw|
method coming from \lstinline|Drawable|, in order to draw a widget
with a deck of cards. Note that hierarchical overriding is denoted in the UML
diagram with the notation
\lstinline|draw()|$\shneg$\lstinline|Drawable|. It expresses that the \lstinline|draw| method from \lstinline|Drawable|
is overridden. Although in this example only one of the
\lstinline|draw| methods is overridden (and the other is simply inherited), hierarchical overriding
supports multiple conflicting methods to be independently overridden as well.

To present hierarchical overriding and dispatching, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness. 
In summary, our contributions are:
\begin{itemize}
	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility in the presence
        of unintentional method conflicts.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics, and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} interpreter in Scala.
\end{itemize}
